---
title: "Function Practice and Geoms"
author: "Genee' Glascoe"
date: "6 April 2020"
output: html_notebook
---
*This notebook is for developing a function and working on geoms*

***
### Question 1

*This function will compute the total score for respondents on a Likert scale*

```{r}
likert_total <- function(surv.data, scale, num.vec) {
  reverse.score <- surv.data[,num.vec] <-(scale+1) - surv.data[,num.vec]
  tot.score.sum <- rowSums(surv.data)
  surv.data$sum <- tot.score.sum
  return(surv.data)
}
```

***
### Question 2

Testing out the function, *likert_total*, that will print out a CSV file which 
contains the orginal data of the CSV file with the total score added.
```{r include=FALSE}
library(here)

activity_surv <- read.csv(here("Data", "Activity Data.csv"))

total_score <- likert_total(activity_surv, 6, c(6, 7, 8))

total_score$ID <- activity_surv$ID

total_score_2 <- total_score[c(1:10)]

write.csv(total_score_2, here("Data", "Total Score.csv"))

```

***
### Question 3

Constructing a single scatterplot showing the relationship of science scores 
to math scores by gender

```{r include=FALSE}
library(tidyverse)
library(here)

hsb2 <- read_csv(here("Data", "hsb2.csv"))

hsb2$female <- factor(hsb2$female,
                   labels = c("female", "male"),
                   ordered = TRUE)
```

```{r} 
ggplot(data = hsb2) +
  geom_point(mapping = aes(x = science, y = math, color = female)) +
  labs(x = "Science Score", y = "Math Score", 
  title = "Relationship between Science and Math Scores by Gender")
```

***
### Question 4

Constructing a seprate scatterplot showing the relationship of science scores 
to math scores by gender

```{r}

ggplot(data = hsb2) +
  geom_point(mapping = aes(x = science, y = math)) +
  labs(x = "Science Score", y = " Math Score", 
  title = "Relationship between Science and Math Scores by Gender") +
  facet_grid(~female)
```

***
### Question 5

A violin gemo is being utilized to compare the distribution of school types 
and science scores by displaying their densities.

```{r}
ggplot(data = hsb2) +
  geom_violin(mapping = aes(x = schtyp, y = science, fill = schtyp, 
                            group = schtyp, color=schtyp)) +
  labs(x = "School Type", y = "Science Score", 
  title = "Relationship between School Type and Science Scores")
```


